---
title: 'Part 3: Parametrized Reporting with RMarkdown and friends'
author: "Ted Laderas"
date: "`r Sys.Date()`"
#output: html_document
output: word_document
#output: slidy_presentation
#output: distill::distill_article()
params: 
  date: !r Sys.Date()
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(quantmod)
library(ggplot2)
library(tidyquant)
library(magrittr)
library(broom)
library(dplyr)
```

## Report for `r params$date`

This is an example of a parametrized report that you can build with RMarkdown.

## The act of knitting

Try clicking the "Knit" button above (You may have to allow the popup or reload it). You will see that the RMarkdown window above is doing what's called "knitting". 

**Knitting** is running code and combining it with the text, or Markdown output. 

## The Powerful thing about RMarkdown

You can output it to many different kinds of outputs. 

Try uncommenting one of the above `output:` lines (make sure to comment the current one out), and try out a different format.

## Streams as Data Sources

Working with process data is working with a *stream* of data. There are some challenges with this:

- Data stream is changing and you need to be responsive
- Not all of the data is available at once
- Data can get stale (become non-useful) as a matter of time

## Working with Stream Data

Whether it be from a database or directly from an instrument, or from an updated spreadsheet, you can specify a stream as a data source.

You can think of a data stream as an infinitely long `data.frame`.

Datastreams can be piped through `ggplot2` or `dplyr` just as well as a static csv file.


## Enter RMarkdown and parametrized reporting

Say you need to produce a daily summary report utilizing data from yesterday. There are various routes to this:

1. Copy paste your R-markdown code, modify each day
2. Have a template report that is automatically knitted each day with yesterday's date as a parameter.

Number 2 is much, much easier and less error prone.


## Parametrized R Markdown

Notice there's a field above called `params`. We're providing today's date as a parameter.


## Get Stock prices

For our data stream, we're going to access stock data using `{tidyquant}`. 

We want to get information about General Mills ("GIS") and Kellogg's ("K"). 

```{r}
tickers = c("GIS", "K")

prices <- tq_get(tickers,
                 from = "2017-01-01",
                 to = params$date,
                 get = "stock.prices")
```

## Automating a parametrized report

More importantly, we can *automate* this using the command line. We can set a script to run at a particular time using a scheduler workflow app such as `cron` (linux). We can set up a command line script called `runReport.R` that contains the following:

```
rmarkdown::render("part3.Rmd")
```

## Running a script on the command line

We can run our script `runReport.R` on the command line using Rscript:

```
Rscript runReport.R
```

More info about RScript/automating tools here: https://support.rstudio.com/hc/en-us/articles/218012917-How-to-run-R-scripts-from-the-command-line

## Sample of the data

```{r}
prices[1:10,]

```


## Plot the stocks from "2017-01-01" to today

```{r}
prices %>%
  select(date, symbol, adjusted) %>%
  ggplot() +
  aes(x=date,
      group=symbol,
      y=adjusted, color=symbol) +
  geom_line()
```

## Some comments on the data

For today, `r params$date`, we see the following information about Kellogg's stock price versus General Mills stock price.



## Packages that are helpful for data streams

- [`{dbplyr}`](https://dbplyr.tidyverse.org/) - if your stream comes from a database, dbplyr will translate it to SQL
- [`{sparklyr}`](https://spark.rstudio.com/) - if your stream is very large, you can use Spark to analyze it. 
- [`{Microsoft365R}`](https://github.com/Azure/Microsoft365R) - access data on Azure/Sharepoint


## Where Next?

There are a lot of directions you can go now.

- You can start modeling your data using [`{tidymodels}`](https://www.tidymodels.org/)
- You can start building interactive reports using [`{shiny}`](https://shiny.rstudio.com)
- You can start building websites with Rmarkdown!

There's a whole wide world out there to learn!

## Stay in Touch

[tedladeras] at [gmail.com]

