---
title: "QPRC Short Course 2021"
author: Ted Laderas
description: |
  Website for the QPRC Short Course on the Tidyverse
site: distill::distill_website
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)

```

## RStudio Workspace

Please message Eric Leung if you do not have access to the project.

# Learning Objectives

## Part 1

1.  **Import** spreadsheet-style data into R as a `data.frame`.
2.  **Visualize** `numeric` vectors in this dataset using `ggplot2`
3.  **Visualize** categorical/numeric variables as `boxplots`
4.  **Customize** your plot using `theme()`
5.  **Change** colors and breaks using `{scales}`

## Part 2

-   **List** 5 key `{dplyr}` verbs for data manipulation
-   **Sort** a dataset by columns using `arrange()`
-   **Select** columns from a dataset using `select()`
-   **Learn** and apply `mutate()` to change the data type of a variable
-   **Apply** `mutate()` to calculate a new variable based on other variables in a `data.frame`.
-   **Apply** `case_when` in a `mutate()` statement to make a continuous variable categorical
-   **Apply** `group_by()/summarize()` as a pattern to get summary statistics, including counts, means, and standard deviations within a category.
-   **Standardize** variable names using `clean_names()`

## Part 3

- **Articulate** the different kinds of output formats in RMarkdown
- **Utilize** YAML front matter to customize an RMarkdown report
- **Utilize** parameters to make reusable reports
- **Use** streams as data sources for an RMarkdown report 

## Intro Slides

```{r}
knitr::include_url("https://laderast.github.io/qprc_short_course_2021/slides/#1")
```

## RMarkdown Slides




