---
title: "QPRC Short Course 2021"
author:
  - first_name: "Ted"
    last_name: "Laderas"
    url: https://laderast.github.io
    affiliation: Principal Scientist and Bioinformatics Trainer, DNAnexus
  - first_name: "Eric"
    last_name: "Leung"
    url: https://erictleung.com/
    affiliation: Data Scientist, Disney
description: |
  Website for the QPRC Short Course on the Tidyverse
site: distill::distill_website
output: 
  distill::distill_article:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)

```

## RStudio Workspace

Please message Eric Leung in Zoom if you do not have access to the Rstudio.cloud project.

# Part 1

## Learning Objectives

1.  **Import** spreadsheet-style data into R as a `data.frame`.
2.  **Visualize** `numeric` vectors in this dataset using `ggplot2`
3.  **Visualize** categorical/numeric variables as `boxplots`
4.  **Customize** your plot using `theme()`
5.  **Change** colors and breaks using `{scales}`

## Slides

Open the introduction slides in a separate window: <a href="https://laderast.github.io/qprc_short_course_2021/slides/#1" target="_blank">https://laderast.github.io/qprc_short_course_2021/slides/#1</a>

```{r}
knitr::include_url("https://laderast.github.io/qprc_short_course_2021/slides/#1")
```

## Further Resources

- [`{ggplot2}` cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/data-visualization-2.1.pdf)



# Part 2

## Learning Objectives

-   **List** 5 key `{dplyr}` verbs for data manipulation
-   **Sort** a dataset by columns using `arrange()`
-   **Select** columns from a dataset using `select()`
-   **Learn** and apply `mutate()` to change the data type of a variable
-   **Apply** `mutate()` to calculate a new variable based on other variables in a `data.frame`.
-   **Apply** `case_when` in a `mutate()` statement to make a continuous variable categorical
-   **Apply** `group_by()/summarize()` as a pattern to get summary statistics, including counts, means, and standard deviations within a category.
-   **Standardize** variable names using `clean_names()`

## Further Resources

- [`{dplyr}` cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf)
- [`{tidyowl}` learnR tutorials](https://github.com/laderast/tidyowl)

# Part 3

## Learning Objectives

- **Articulate** the different kinds of output formats in RMarkdown
- **Utilize** YAML front matter to customize an RMarkdown report
- **Utilize** parameters to make reusable reports
- **Use** streams as data sources for an RMarkdown report 

## RMarkdown Slides

Open the Rmarkdown slides in a separate window: <a href="https://laderast.github.io/qprc_short_course_2021/slides/rmarkdown.html#1" target="_blank">https://laderast.github.io/qprc_short_course_2021/slides/rmarkdown.html#1</a>

```{r}
knitr::include_url("https://laderast.github.io/qprc_short_course_2021/slides/rmarkdown.html#1")
```

## Further Resources

- [RMarkdown at RStudio](https://rmarkdown.rstudio.com/)
- [RMarkdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/)

```{r}
knitr::include_url("https://slides.djnavarro.net/starting-rmarkdown/#1")
```